### 2021-02-21 paper.tex
Add TP orcid and adjust .gitignore.
Expand related work and some comments plus small corrections.

%===========[ TITLES ]==========================================================
%Chnage to your own information
%\newcommand{\contribtitle}{FAIR Knowledge Graphs for the Management of Health Information Systems}
\newcommand{\contribtitle}{SNIK Graph}
\newcommand{\contribsubtitle}{Visualizing Knowledge about Management of Hospital Information Systems}
%\newcommand{\contribsubtitle}{Graph-Based Exploration of an Hospital Information Systems}
\newcommand{\firstauthor}{Konrad Höffner\textsuperscript{1[https://orcid.org/0000-0001-7358-3217]}}
\newcommand{\firstauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\secondauthor}{Thomas Pause\textsuperscript{2[https://orcid.org/1111-2222-3333-4444]}\todo{Thomas: deine orcid ggnf. erstellen und hier eintragen }}
\newcommand{\secondauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\thirdauthor}{Franziska Jahn\textsuperscript{3[https://orcid.org/0000-0002-7687-8544]}}%\todo{fj: orcid bitte anpassen}
\newcommand{\thirdauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}

@@

\todo{thomas continues the use cases from the book (only list those that are supported)}
SNIK Graph supports the following use cases:

UC1 / UC4
The visualization of the complete T-Box (UC1) / A-Box (UC4).
The global view of the 4117 classes of SNIK, their connecting triplse 12115 triples and the 73 instances is shown on startup in SNIK Graph in the main tab, however due to overplotting, this view is mostly used as as an entry point to the search or to execute the star operations (see section \enquote{Star}) that spawn a subgraph in another tab.

@@

UC N...

UC15

\todo{thomas, please finish this section using some similar tools from the bachelor thesis}
%Users should see the structure of the whole graph at once, but also be able to start at a certain resource and explore its neighbourhood incrementally.

%In the course of the SNIK project

@@

\subsection*{Role Use}
\todo{konrad an alle: was mache ich mit der sparql query? rausschmeissen, drin lassen oder umbauen?}
\begin{figure}[h]
\begin{lstlisting}
SELECT DISTINCT ?inner ?middle ?outer ?outerx {
 <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
 ?inner meta:subTopClass meta:Role.
 OPTIONAL {
  ?inner ?p ?middle.
  ?middle meta:subTopClass meta:Function.
  OPTIONAL {
   ?middle ?q ?outer.
   ?outer meta:subTopClass meta:EntityType.
   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
}}}
\end{lstlisting}
\caption{SPARQL query to generate the \emph{role use} visualization.}
\label{lst:roleuse}
\end{figure}
\vspace{-3pt}
A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles, see \Cref{fig:classuse}:

>>>>

%===========[ TITLES ]==========================================================
%Chnage to your own information
%\newcommand{\contribtitle}{FAIR Knowledge Graphs for the Management of Health Information Systems}
\newcommand{\contribtitle}{SNIK Graph}
\newcommand{\contribsubtitle}{Visualizing Knowledge about Management of Hospital Information Systems}
%\newcommand{\contribsubtitle}{Graph-Based Exploration of an Hospital Information Systems}
\newcommand{\firstauthor}{Konrad Höffner\textsuperscript{1[https://orcid.org/0000-0001-7358-3217]}}
\newcommand{\firstauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\secondauthor}{Thomas Pause\textsuperscript{2[https://orcid.org/0000-0001-5832-4890]}}
\newcommand{\secondauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\thirdauthor}{Franziska Jahn\textsuperscript{3[https://orcid.org/0000-0002-7687-8544]}}%\todo{fj: orcid bitte anpassen}
\newcommand{\thirdauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}

@@

SNIK Graph supports the following use cases:

UC1 / UC4
The visualization of the complete T-Box (UC1) / A-Box (UC4).
The global view of the 4117 classes of SNIK, their connecting 12115 triples and the 73 instances is shown on startup in SNIK Graph in the main tab, however due to overplotting, this view is mostly used as as an entry point to the search or to execute the star operations (see section \enquote{Star}) that spawn a subgraph in another tab.

@@

UC6
The visualization of the instances belonging to a specific class.
The instances in SNIK Graph are shown near their specific class(es). \todo{Konrad: stimmt das so? hier war ich mir sehr unsicher}

UC7
The visualization of the paths that link different instances.
Several path operations can be used in SNIK Graph to explore the connections between instances.

UC8
The exploration of the dataset.
Besides the global view, SNIK Graph supports exploratory search and exploration of the knowledge graph.
A fulltext search helps users to find their start ressource, path and expand operations leads them to an interesting exploration.

UC13-15
Filtering.
SNIK Grah provides several filter options.
Users can decide which sources (textbook) to use, what kinds of types depending on our meta model do display and can also filter along relations.

The specific use case of SNIK Graph is, that users should see the structure of the whole graph at once, but also be able to start at a certain resource and explore its neighbourhood incrementally.
It also has to be a web application, to be platform-independent.
For better availability and adoption around stakeholders (especially teachers and students) it also has to be free and open source.
Our research along other tools does not provide a proper fitting solution.
\todo{konrad: ich denke das reicht hierzu aus, es geht doch nur darum zu zeigen wieso wir nicht tool xyz nutzen sondern unser eigenes machen oder? und die Auflistung der erfüllten usecases passt mMn auch sehr gut dazu}
%In the course of the SNIK project

@@

\subsection*{Role Use}
\todo{konrad an alle: was mache ich mit der sparql query? rausschmeissen, drin lassen oder umbauen? TP: drinlassen, aber direkt ans Bild hängen.. Sowas wie aus der Query folgt dieses Bild. Ich finde sowas sollte schon rein ins Paper}
\begin{figure}[h]
\begin{lstlisting}
SELECT DISTINCT ?inner ?middle ?outer ?outerx {
 <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
 ?inner meta:subTopClass meta:Role.
 OPTIONAL {
  ?inner ?p ?middle.
  ?middle meta:subTopClass meta:Function.
  OPTIONAL {
   ?middle ?q ?outer.
   ?outer meta:subTopClass meta:EntityType.
   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
}}}
\end{lstlisting}
\caption{SPARQL query to generate the \emph{role use} visualization.}
\label{lst:roleuse}
\end{figure}
\vspace{-3pt}
A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles, see \Cref{fig:classuse}:
